|

### 2019-08-30 paper.Rmd
Adding plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

XXX Example 2x2, row 1-col 1 has a slice projection  of a solid 4D spehere, row 1-col 2 has a slice projectionof a hollow 4D sphere; row 2-col 1 has a slice projection of a  solid 4D cube, row 1-col 2 has a slice projection of a hollow 4D cube

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

@@

```{r renderFunction, echo=FALSE, eval=TRUE, warning=FALSE, fig.height=1.5, fig.width = 5.5, fig.cap="Projected slices through 4d geometric shapes. On the left a full (hollow) hypersphere (a, b), on the right a full (hollow) hypercube (c, d). Points inside the slice are shown as black bullets, points outside the slice are shown as grey dots. We can clearly distinguish the full from the hollow objects based on the slice display."}
library(tidyverse)

# slight modification of the function in tourr::display_slice
render_data <- function(data, proj, h, anchor) {
    # Render projected points
    x <- data %*% proj
    d <- tourr::anchored_orthogonal_distance(proj, data, anchor)
    pch <- rep(46, nrow(x))
    pch[d < h] <- 20
    col <- rep("grey", nrow(x))
    col[d < h] <- "black"
    ggplot() +aes(x[,1], x[,2]) + geom_point(pch = pch, color=col) + theme_void() + coord_fixed()
}

anchor <- rep(0, 4)
plane <- tourr::basis_init(4, 2)
nPt <- 5000

set.seed(3008)

d1 <- geozoo::sphere.solid.random(4, nPt)$points
d2 <- geozoo::sphere.hollow(4, nPt)$points
d3 <- geozoo::cube.solid.random(4)$points[1:nPt,] %>% scale(scale = FALSE)
d4 <- geozoo::cube.face(4)$points[1:nPt,] %>% scale(scale = FALSE)

a <- render_data(d1, plane, 0.2, anchor) + labs(title="a")
b <- render_data(d2, plane, 0.2, anchor) + labs(title="b")
c <- render_data(d3, plane, 0.2, anchor) + labs(title="c")
d <- render_data(d4, plane, 0.2, anchor) + labs(title="d")

library(gridExtra)
grid.arrange(a, b, c, d, nrow=1)

```
